---
title: "Violin following study stats - master"
author: "Lucas Klein"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: 
    keep_tex: yes
  #keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

knitr::opts_knit$set(root.dir = "/Users/lucas/Desktop/Following/ANALYSIS/Stats/")
```


# Prep and load

```{r load, message=FALSE, results='hide'}
setwd("/Users/lucas/Desktop/Following/ANALYSIS/Stats/")
imageDirectory <- "/Users/lucas/Desktop/Following/Manuscript/Images/"

# necessary
library(readr) # for reading in csv files
library(dplyr); library(plyr)
library(reshape)
library(emmeans)
library(lme4)
library(lmerTest)
library(effects)
library(utils)
library(ggplot2)
library(ggpubr) # for arranging plots
library(grid)
library(effectsize)
library(r2glmm)

# possibly not necessary?
# library(lsr)
# library(Rmisc)
# library(psych)
# library(magrittr)
```

Two pieces:

```{r echo=TRUE}
piece1 <- "Danny Boy"
piece2 <- "In The Garden"
section <- "whole" # Which section?
```

```{r}
# Import in wide format, with CC values
filename1 <- paste("following_",piece1,"_",section,".csv",sep='')
filename2 <- paste("following_",piece2,"_",section,".csv",sep='')

following1 <- read.csv(filename1, header = TRUE, na.strings = c("","NA")) # E.g. "following_Danny Boy_22_1.csv"
following2 <- read.csv(filename2, header = TRUE, na.strings = c("","NA")) # E.g. "following_Danny Boy_22_1.csv"
following1_lag0 <- read.csv("following_Danny Boy_whole_lag0.csv", header = TRUE, na.strings = c("","NA"))
following2_lag0 <- read.csv("following_In The Garden_whole_lag0.csv", header = TRUE, na.strings = c("","NA"))

#ccorr <- read.csv("ccorr.csv", header = TRUE, na.strings = c("", "NA"))

#summary(following1)
#summary(following2)
#str(following) # make sure all columns are the correct data type

# OPTIONAL: Choose a subset of trials to analyze
#following1 <- following1[following1$Trial %in% c(1,2,3), ]
#following2 <- following2[following2$Trial %in% c(1,2,3,4,5), ]

```

Any NA's?

```{r}
# Are there any NAs?
print(colSums(is.na(following1)))
print(colSums(is.na(following2)))
```
### Pre-process

Both dataframes are currently in wide format, with a column for cross-correlation values. This removes the CC column and creates long-formatted dataframes for both pieces, including a combined version of both together. Then outputs these three dataframes in a list.

Recording to performance direction = 1
Performance to recording direction = 2

```{r}
# Make Trial and Participant factors
## This is necessary for reshaping the data correctly
# following1$Trial <- factor(following1$Trial, ordered = TRUE)
# following1$Participant <- factor(following1$Participant, ordered = FALSE)
# 
# following2$Trial <- factor(following2$Trial, ordered = TRUE)
# following2$Participant <- factor(following2$Participant, ordered = FALSE)

following1$CC0 <- following1_lag0$CC
following2$CC0 <- following2_lag0$CC

source("Scripts/prep_following.R")
dfs <- prep_following(following1, following2) # list of 3 items: lf1, lf2, lf_comb

lf1 <- dfs[[1]] # GC values in long format (both directions): piece 1
lf2 <- dfs[[2]] # " " : piece 2
cc1 <- dfs[[3]] # CC values, piece 1
cc2 <- dfs[[4]] # CC values, piece 2

# In these data frames, another column has been added for Piece (1 or 2) and data from both pieces concatenated
lf_comb <- dfs[[5]] # GC values in long format for both pieces
cc_comb <-  dfs[[6]] # CC values for both pieces

num_participants <- length(unique(lf_comb$Participant)) # 8
```



Now separate by playing experience: folk players vs. non-folk players.

```{r}
# SEPARATING BY PLAYING EXPERIENCE

# if(piece == "Danny Boy") {
#   folk <- filter(lf, Participant %in% c(4,5,8))
#   nonfolk <- filter(lf, Participant %in% c(1,2,3,6,7))
#   ear <- filter(lf, Participant %in% c(2,3,4,5,8))
#   nonear <- filter(lf, Participant %in% c(1,6,7))
# } else {
#   players <- filter(lf, Participant %in% c(3,4,5,6))
#   nonfolk <- filter(lf, Participant %in% c(1,2,7,8))
#   ear <- filter(lf, Participant %in% c(1,2,3,4,5,6))
#   nonear <- filter(lf, Participant %in% c(7,8))
# }
```



# Plots

Set title based on piece and section

```{r}
# If analyzing one piece at a time:
piece <- "Danny Boy"

# Title for whole piece
if(piece == "Danny Boy" && section == "whole") {
  plot_title <- "Piece 1: Danny Boy"
} else {
  plot_title <- "Piece 2: In The Garden"
}

# Auto
#plot_title1 <- paste(piece," - ","section ",section,sep = '')
#plot_title <- paste("Section ",section,sep = '')
# Manual
#plot_title <- "In The Garden - 'by ear' players"

# Make plots
source("Scripts/plots_following.R")
#source("Scripts/multiplot.R")
plots <- plots_following(dfs)
```


## GC values by direction

```{r violin, fig.height=4.5, fig.width=7}
violin_all <- ggarrange(plots[[7]], plots[[8]],
          common.legend = TRUE,
          legend = "bottom",
          labels = c('A','B'))
violin_all

ggsave(paste(imageDirectory,"violin.jpg", sep=''), violin_all)
```

Figure \ref{fig:violin} shows.....


## GC and CC by trial

```{r GC_combined, fig.height=4.5, fig.width=7}
plot_names <- c('1' = "Danny Boy",
                '2' = "In The Garden")

GC_combined <- plots[[5]] + facet_wrap(~Piece, labeller = as_labeller(plot_names)) #"label_both")
GC_combined
ggsave(paste(imageDirectory,"GC_combined.jpg",sep=''),GC_combined)
```


```{r CC_all, fig.height=7, fig.width=6.5}
plot_names <- c('1' = "Danny Boy",
                '2' = "In The Garden")

CC_combined <- plots[[6]] + facet_wrap(~Piece, labeller = as_labeller(plot_names))

CC_combined_0lag <- plots[[13]] + facet_wrap(~Piece, labeller = as_labeller(plot_names))

CC_all <- ggarrange(CC_combined, CC_combined_0lag, ncol = 1,
                       labels = c('A','B'))
#  theme(legend.position = "none")

CC_all

#mplot <- multiplot(plotlist=plots,layout=matrix(c(1,2),nrow=1,byrow=TRUE))

ggsave(paste(imageDirectory,"CC_all.jpg",sep=''),CC_all)
```

Figure \ref{fig:allplots} shows

### GC for individual participants

```{r gc_parts, eval=FALSE, fig.height=5.5, fig.width=8}
plots[[9]] # plots of GC values for each participant, Piece 1
plots[[10]] # plots of GC values for each participant, Piece 2
plots[[6]]
```


# Stats

## Information flow direction

### T-tests between directions

```{r}
t.test_piece1 <- t.test(
  filter(lf1,Direction=="Recording to Performance")$GC,
  filter(lf1,Direction=="Performance to Recording")$GC,
  paired = T,
  alternative = "two.sided")

t.test_piece2 <- t.test(
  filter(lf2,Direction=="Recording to Performance")$GC,
  filter(lf2,Direction=="Performance to Recording")$GC,
  paired = T,
  alternative = "two.sided")

print(paste('Danny Boy: t = ', round(t.test_piece1$statistic, digits = 3),', p = ',t.test_piece1$p.value))

print(paste('In The Garden: t = ', round(t.test_piece2$statistic, digits = 3),', p = ',t.test_piece2$p.value))


DBtt_stat <- round(t.test_piece1$statistic, digits = 3)
DBtt_pval <- t.test_piece1$p.value

ITGtt_stat <- round(t.test_piece2$statistic, digits = 3)
ITGtt_pval <- t.test_piece2$p.value
```




## Changes in GC and CC across trials

### Linear mixed effects mdodels
- lmer() function
- Automatically uses Type III SS

r2beta: r2beta Compute R Squared for Mixed Models
t-value: slope is significantly NOT zero
Estimate: slope of model, effect size
chi squared - compares error

(What does it mean for fixed effects to be correlated?)


```{r}
# Prep
source("Scripts/lmer_following.R")
#lf1$Trial <- as.integer(lf1$Trial)
#lf2$Trial <- as.integer(lf2$Trial)
#lf_comb$Trial <- as.integer(lf_comb$Trial)
#cc_comb$Trial <- as.integer(cc_comb$Trial)

# For lmer modeling, only use recording to performance
lf1_r2p <- subset(lf1, Direction == "Recording to Performance")
lf2_r2p <- subset(lf2, Direction == "Recording to Performance")
lf_comb_r2p <- subset(lf_comb, Direction == "Recording to Performance")

# Each output from lmer_following is a LIST of models
# ~~~~~ GRANGER CAUSALITY ~~~~~
mod.gc1 <- lmer_following(lf1_r2p) # Danny Boy
mod.gc2 <- lmer_following(lf2_r2p) # In The Garden
mod.gcc <- lmer_following(lf_comb_r2p) # both

# ~~~~~ CROSS-CORRELATION ~~~~~
mod.cc1 <- lmer_following(cc1)
mod.cc2 <- lmer_following(cc2)
mod.ccc <- lmer_following(cc_comb)
```

### Linear models for Granger causality

```{r}
#mod.gc1[[2]]
#mod.gc2[[2]]

# ANOVAs between full (2) vs. reduced (1)
anova.gc1 <- anova(mod.gc1[[1]], mod.gc1[[2]]) # p-value
anova.gc2 <- anova(mod.gc2[[1]], mod.gc2[[2]]) # p-value 
#summary(mod.gc1[[2]])
# confint(mod.gc1[[2]])
# ranef(mod.gc1[[2]]) # Trial = -0.001646372
# anova(mod.gc1[[2]])

# Define variables to report in results
DBm_beta <- round(fixef(mod.gc1[[2]])[2], digits=3)
DBm_rsq <- round(r2beta(mod.gc1[[2]], method = 'kr')[[7]][1], digits=3) # or 'nsj'
DBm_pval <- round(anova.gc1$`Pr(>Chisq)`[2], digits=3)

ITGm_beta <- round(fixef(mod.gc2[[2]])[2], digits=3)
ITGm_rsq <- round(r2beta(mod.gc2[[2]], method = 'kr')[[7]][1], digits=3) # or 'nsj'
ITGm_pval <- round(anova.gc2$`Pr(>Chisq)`[2], digits=3)
```

#### Results

```{r}
print(paste('Danny Boy: beta = ',DBm_beta,' R-squared = ',DBm_rsq,' p-value = ',DBm_pval))

print(paste('ITG: beta = ',ITGm_beta,' R-squared = ',ITGm_rsq,' p-value = ',ITGm_pval))
```


```{r, eval=FALSE}
# Dobri's method:
# First, run anova on all models to find the best one
## Anova finds differences in variance explained by each model compared to the model that is slightly less comple. So it compares models in order of complexity (# of terms)

# mod <- mod.cc1[[2]] # change this
# parameters::model_parameters(mod, effects = "fixed", ci_method = "satterthwaite")
# t <- parameters::model_parameters(mod, effects = "fixed", ci_method = "satterthwaite")[7][[1]]
# dfs <- parameters::model_parameters(mod, effects = "fixed", ci_method = "satterthwaite")[8][[1]]
# t_to_omega2(t[1],df=dfs[1])
# t_to_omega2(t[2],df=dfs[2])

#Jesse's:

#model = glmer(primacy ~ 1 + modality * list_length * pres_rate + (1|subject), data=e1_data, family='binomial', control=glmerControl(optimizer = "bobyqa"))
#Anova(model, type=3)
```


```{r}
# ~~~~~ Pieces combined ~~~~~
#anova(mod.gcc[[7]])
#anova(mod.gcc[[6]],mod.gcc[[5]])

#print(anova(mod.gcc[[1]],mod.gcc[[2]],mod.gcc[[3]],mod.gcc[[4]],mod.gcc[[5]],mod.gcc[[6]],mod.gcc[[7]],mod.gcc[[8]]))

#anova(mod.gcc[[3]], mod.gcc[[7]], mod.gcc[[8]])
#anova(mod.gcc[[7]], mod.gcc[[8]])

#fixef(mod.gcc[[7]])
#confint(mod.gcc[[7]])
#ranef(mod.gcc[[7]]) # Trial = -0.001646372
#anova(mod.gcc[[7]])
```


### Linear models for Cross-correlation - ALL LAGS

```{r}
# Linear mixed model fit by max likelihood
#mod.cc1[[2]] # beta estimate
#mod.cc2[[2]] # beta estimate

# ANOVAs between full (2) vs. reduced (1)
anova.cc1 <- anova(mod.cc1[[1]], mod.cc1[[2]]) # p-value
anova.cc2 <- anova(mod.cc2[[1]], mod.cc2[[2]]) # p-value 
#summary(mod.gc1[[2]])
# confint(mod.gc1[[2]])
# ranef(mod.gc1[[2]]) # Trial = -0.001646372
# anova(mod.gc1[[2]])

# Define variables to report in results
DBmcc_beta <- round(fixef(mod.cc1[[2]])[2], digits = 3)
DBmcc_rsq <- round(r2beta(mod.cc1[[2]], method = 'kr')[[7]][1], digits = 3) # or 'nsj'
DBmcc_pval <- round(anova.cc1$`Pr(>Chisq)`[2], digits = 3)

ITGmcc_beta <- round(fixef(mod.cc2[[2]])[2], digits = 3)
ITGmcc_rsq <- round(r2beta(mod.cc2[[2]], method = 'kr')[[7]][1], digits = 3) # or 'nsj'
ITGmcc_pval <- round(anova.cc2$`Pr(>Chisq)`[2], digits = 3)
```


#### Results

```{r}
print(paste('Danny Boy: beta = ',DBmcc_beta,' R-squared = ',DBmcc_rsq,' p-value = ',DBmcc_pval))

print(paste('In The Garden: beta = ',ITGmcc_beta,' R-squared = ',ITGmcc_rsq,' p-value = ',ITGmcc_pval))
```


### Linear models for Cross-correlation - 0 LAG (synchrony)

```{r}
# Linear mixed model fit by max likelihood
#mod.cc1[[10]] # beta estimate
#mod.cc2[[10]] # beta estimate

# ANOVAs between full (2) vs. reduced (1)
anova.cc01 <- anova(mod.cc1[[9]], mod.cc1[[10]]) # p-value
anova.cc02 <- anova(mod.cc2[[9]], mod.cc2[[10]]) # p-value 
#summary(mod.gc1[[2]])
# confint(mod.gc1[[2]])
# ranef(mod.gc1[[2]]) # Trial = -0.001646372
# anova(mod.gc1[[2]])

# Define variables to report in results
DBmcc0_beta <- round(fixef(mod.cc1[[10]])[2], digits=3)
DBmcc0_rsq <- round(r2beta(mod.cc1[[10]], method = 'kr')[[7]][1], digits = 3) # or 'nsj'
DBmcc0_pval <- round(anova.cc01$`Pr(>Chisq)`[2], digits = 3)

ITGmcc0_beta <- round(fixef(mod.cc2[[10]])[2], digits = 3)
ITGmcc0_rsq <- round(r2beta(mod.cc2[[10]], method = 'kr')[[7]][1], digits = 3) # or 'nsj'
ITGmcc0_pval <- round(anova.cc02$`Pr(>Chisq)`[2], digits = 3)
```

#### Results

```{r}
print(paste('Danny Boy: beta = ',DBmcc0_beta,' R-squared = ',DBmcc0_rsq,' p-value = ',DBmcc0_pval))

print(paste('In The Garden: beta = ',ITGmcc0_beta,' R-squared = ',ITGmcc0_rsq,' p-value = ',ITGmcc0_pval))
```


## Trend Analysis

Calculating linear contrasts (comparisons) among levels of a quantitative (ordered) factor
Assumes equal subjects in each group

Trend analysis partitions the sum of squares for the model into portions due to linear trend, quadratic trend, cubic trend, etc. If there are k groups it is possible to look at up to k - 1 trends, although often researchers combine together all trends above quadratic or cubic.


### Trend analysis of Granger causality

```{r, results='hide'}
# Prep
contr.poly(n = 8, scores = c(1, 2, 3, 4, 5, 6, 7, 8)) # This command automatically sets up orthogonal contrasts
# These trend contrasts form an orthogonal set

following1$Trial <- factor(following1$Trial, ordered = TRUE) # Danny Boy
#class(following1$Trial) # make sure Trial is an ordered factor
#unique(following1$Trial) # 8 factors
following1_last <- following1[following1$Trial %in% c(5,6,7,8), ]

following2$Trial <- factor(following2$Trial, ordered = TRUE) # In The Garden
#class(following2$Trial) # make sure Trial is an ordered factor
#unique(following2$Trial) # 8 factors
following2_last <- following2[following2$Trial %in% c(5,6,7,8), ]
```

#### Results

```{r}
aov.gc1 <- aov(GC_r2p ~ Trial, data = following1) # piece 1
aov.gc2 <- aov(GC_r2p ~ Trial, data = following2) # piece 2

DBaov_summary <- summary(aov.gc1, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))
ITGaov_summary <- summary(aov.gc2, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))

DBaov_df <- 1
DBaov_dfres <- aov.gc1$df.residual
DBaov_F <- round(DBaov_summary[[1]][2,4], digits = 3)
DBaov_pval <- round(DBaov_summary[[1]][2,5], digits = 3)

ITGaov_df <- 1
ITGaov_dfres <- aov.gc2$df.residual
ITGaov_F <- round(ITGaov_summary[[1]][2,4], digits = 3)
ITGaov_pval <- round(ITGaov_summary[[1]][2,5], digits = 3)

```


```{r}
print(paste('Danny Boy: F(',DBaov_df,',',DBaov_dfres,') = ',DBaov_F,' with p = ',DBaov_pval))
print(paste('In The Garden: F(',ITGaov_df,',',ITGaov_dfres,') = ',ITGaov_F,' with p = ',ITGaov_pval))
```


### Trend analysis of Cross-correlation

#### ALL LAGS

```{r}
aov.cc1 <- aov(CC ~ Trial, data = following1) # piece 1
aov.cc2 <- aov(CC ~ Trial, data = following2) # piece 2

DBaovcc_summary <- summary(aov.cc1, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))
ITGaovcc_summary <- summary(aov.cc2, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))

DBaovcc_df <- 1
DBaovcc_dfres <- aov.cc1$df.residual
DBaovcc_F <- round(DBaovcc_summary[[1]][2,4], digits = 3)
DBaovcc_pval <- round(DBaovcc_summary[[1]][2,5], digits = 3)

ITGaovcc_df <- 1
ITGaovcc_dfres <- aov.cc2$df.residual
ITGaovcc_F <- round(ITGaovcc_summary[[1]][2,4], digits = 3)
ITGaovcc_pval <- round(ITGaovcc_summary[[1]][2,5], digits = 3)

# not significant
```

```{r}
print(paste('Danny Boy: F(',DBaovcc_df,',',DBaovcc_dfres,') = ',DBaovcc_F,' with p = ',DBaovcc_pval))
print(paste('In The Garden: F(',ITGaovcc_df,',',ITGaovcc_dfres,') = ',ITGaovcc_F,' with p = ',ITGaovcc_pval))
```


#### 0 LAG

```{r}
aov.cc01 <- aov(CC0 ~ Trial, data = following1) # piece 1
aov.cc02 <- aov(CC0 ~ Trial, data = following2) # piece 2

DBaovcc0_summary <- summary(aov.cc01, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))
ITGaovcc0_summary <- summary(aov.cc02, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))

DBaovcc0_df <- 1
DBaovcc0_dfres <- aov.cc01$df.residual
DBaovcc0_F <- round(DBaovcc0_summary[[1]][2,4], digits = 3)
DBaovcc0_pval <- round(DBaovcc0_summary[[1]][2,5], digits = 3)

ITGaovcc0_df <- 1
ITGaovcc0_dfres <- aov.cc02$df.residual
ITGaovcc0_F <- round(ITGaovcc0_summary[[1]][2,4], digits = 3)
ITGaovcc0_pval <- round(ITGaovcc0_summary[[1]][2,5], digits = 3)
```

```{r}
print(paste('Danny Boy: F(',DBaovcc0_df,',',DBaovcc0_dfres,') = ',DBaovcc0_F,' with p = ',DBaovcc0_pval))
print(paste('In The Garden: F(',ITGaovcc0_df,',',ITGaovcc0_dfres,') = ',ITGaovcc0_F,' with p = ',ITGaovcc0_pval))
```


#### 0 LAG - last four trials

```{r}
aov.cc01L <- aov(CC0 ~ Trial, data = following1_last) # piece 1
aov.cc02L <- aov(CC0 ~ Trial, data = following2_last) # piece 2

DBaovcc0L_summary <- summary(aov.cc01L, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))
ITGaovcc0L_summary <- summary(aov.cc02L, split = list(Trial = list(linear=1, quadratic=2, cubic=3, quartic=4)))

DBaovcc0L_df <- 1
DBaovcc0L_dfres <- aov.cc01L$df.residual
DBaovcc0L_F <- round(DBaovcc0L_summary[[1]][2,4], digits = 3)
DBaovcc0L_pval <- round(DBaovcc0L_summary[[1]][2,5], digits = 3)

ITGaovcc0L_df <- 1
ITGaovcc0L_dfres <- aov.cc02L$df.residual
ITGaovcc0L_F <- round(ITGaovcc0L_summary[[1]][2,4], digits = 3)
ITGaovcc0L_pval <- round(ITGaovcc0L_summary[[1]][2,5], digits = 3)
```

```{r}
print(paste('Danny Boy: F(',DBaovcc0L_df,',',DBaovcc0L_dfres,') = ',DBaovcc0L_F,' with p = ',DBaovcc0L_pval))
print(paste('In The Garden: F(',ITGaovcc0L_df,',',ITGaovcc0L_dfres,') = ',ITGaovcc0L_F,' with p = ',ITGaovcc0L_pval))
```



## Log-fit for CC

#### Danny Boy

```{r}
plot(following1$Trial, following1$CC)
x <- as.integer(following1$Trial)
y <- following1$CC
log.fit <- lm(y ~ log(x))
summary(log.fit)

```

#### In The Garden

```{r}
plot(following2$Trial, following2$CC)
x <- as.integer(following2$Trial)
y <- following2$CC
log.fit <- lm(y ~ log(x))
summary(log.fit)

```


```{r, eval=FALSE}
#trials <- as.integer(unique(following2$Trial))
trials <- following2$Trial
yy <- predict(log.fit, newdata = list(trials), interval = "confidence")
#matlines(trials, yy, lwd=2)

thm <- theme(panel.grid.major.x = element_line(),
             panel.grid.major.y = element_line(),
             plot.title = element_text(size=18, vjust=.5, hjust = .5),
             legend.title = element_text(size=14, hjust = .5),
             legend.key.size = unit(0.5, "cm"),
             legend.text = element_text(size=10),
             legend.background = element_rect(color = "black"),
             legend.position = "bottom",
             axis.title = element_text(size=14),
             axis.title.y = element_text(vjust=1),
             axis.title.x = element_text(vjust=1),
             axis.text = element_text(size=10, colour="black"))

cc.fit <- ggplot(following2, aes(Trial, CC)) +
  geom_point() +
  ggtitle("In The Garden") +
  thm

cc.fit
```


## Correlations between GC and CC

```{r corr, eval=FALSE, fig.height=8, fig.width=7}
# Both pieces
rhos1 <- vector()
rhos2 <- vector()
for (p in 1:8) {
  dat1 <- following1[following1$Participant == p, ]
  dat2 <- following2[following2$Participant == p, ]
  corrs1 <- with(dat1,cor.test(x=GC_r2p, y=CC, method="pearson"))
  corrs2 <- with(dat2,cor.test(x=GC_r2p, y=CC, method="pearson"))
  rhos1[p] <- corrs1$estimate
  rhos2[p] <- corrs2$estimate
}

plot(rhos1)
plot(rhos2)

#cor(following1$GC_r2p, following1$CC, method = "pearson")
```

### Different method

#### Danny Boy
```{r corr1, eval=FALSE, fig.height=8, fig.width=7}
cor_mod1 <- lm(GC_r2p ~ CC, data=following1)
summary(cor_mod1) # same as above

ggplot(following1, aes(GC_r2p, CC)) +
  geom_point() +
  geom_abline()

corr_plot1 <- ggplot(GC_r2p ~ CC, data=following1, type='p', xlab='CC', ylab='GC', main='DB')
  abline(cor_mod1)
```

#### In The Garden
```{r corr2, eval=FALSE, fig.height=8, fig.width=7}
with(following2,cor.test(x=GC_r2p, y=CC, method="pearson"))
with(following2,cor.test(x=GC_r2p, y=CC, method="spearman", exact=F))

cor_mod2 <- lm(GC_r2p ~ CC, data=following2)
summary(cor_mod2) # same

corr_plot2 <- plot(GC_r2p ~ CC, data=following2, type='p', xlab='CC', ylab='GC') +
  abline(cor_mod2) +
  title("ITG")

ggsave(paste(imageDirectory,"corr_plot1.png",sep=''),corr_plot1)
ggsave(paste(imageDirectory,"corr_plot2.png",sep=''),corr_plot2)
```



# Save data

Save entire workspace image (all variables) as .Rdata file
Save data frames as .rda files

```{r}
## SAVE DATA
save.image("/Users/lucas/Desktop/Following/ANALYSIS/Manuscript/following.Rdata")
save(dfs, file = "following.rda")

#save(following, file=paste("following_",piece,"_",section,".rda",sep=''))
#save(long_following, file = paste("long_following_",piece,"_",section,".rda",sep=''))
```


